---
title: "Assignment 3 Data 607"
author: "Al Haque"
date: "Feb 17,2022`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(stringr)
Major <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv",header=TRUE,sep=",")
head(Major)
```

### Exercise 1

Using str_detect to return any pattern I found that in the majors list we have DATA returned once and STATISTICS returned twice. 

```{r}

Major1 <- Major %>%
  select(Major) %>%
  filter(str_detect(Major,"(DATA|STATISTICS)")) 

Major1
```


### Exercise 2



```{r}
Fruits <- c("bell pepper","bilberry","blackberry","blood orange","blueberry","cantaloupe","chili pepper","cloudberry","elderberry","lime","lychee","mulberry","olive","salal berry")
dput(Fruits)
```


### Exercise 3 (14.3.5.1)

#### Exercise 3a

  (.)\1\1 this matches any expressions that have the same letters three times. 


#### Exercise 3b

  "(.)(.)\\2\\1" returns a pair of letters and the pair of letters but reversed ex: peppers

#### Exercise 3c

  (..)\1 finds any expression in which any 2 characters are repeated
  
#### Exercise 3d
  
  "(.).\\1.\\1" returns a string with a character then another character, the same character with any other character,and the original character again. ex: "acada" 
  
#### Exercise 3e

  "(.)(.)(.).*\\3\\2\\1" returns three character followed by zero or more characters with the same three character but reversed. ex: "abccba"


### Exercise 4 (14.3.5.2)


#### Exercise 4a

```{r}

str_subset(words,"^(.)((.*\\1$)|\\1$)")

```


#### Exercise 4b


```{r plot-prop-boys-present}
str_view("church", "([A-Za-z][A-Za-z]).*\\1")
```

#### Exercise 4c

```{r}
str_view("eleven","([a-z]).*\\1.*\\1.")
```


